%  can also ship a program that acts as a virtual machine and thus run other languages in webassembly today

WebAssembly\footnote{https://webassembly.org/} (Wasm) is described by \textcite{Watt2018,JangdaPowersGuhaBerger2019} as a low-level language designed to become a universal compilation target for the web. According to it's original authors \textcite{HaasRossbergSchuffTitzerHolmanGohmanWagnerZakaiBastien2017} it's a portable assembly-language for web browsers and future adaptations. Technically WebAssembly is bytecode created by \emph{compiling} (any form of) code to WebAssembly \parencite{Watt2018} which then can be executed in any WebAssembly-engine. This can be compared with JavaScript-code that is \emph{interpreted} while running inside a JavaScript-engine.

WebAssembly can be seen as a successor to earlier technologies such as asm.js from Mozilla (previously discussed) and Native Client (NaCL) from Google. NaCL executes native code in a separate part of Chrome and asm.js  \parencite{Zakai2018} is a subset of JavaScript optimized for performance \parencite{VanEsNicolayStievenartDHondtDeRoover2016} and can be interpreted in any web browser.

% WebAssembly can be seen as the forth core web technology as illustrated in Figure \ref{figure:webtechnologies-timeline}. It's the first web technology since 1996 to be universally adopted by all major web browser vendors \parencite{HaasRossbergSchuffTitzerHolmanGohmanWagnerZakaiBastien2017}.

% WebAssembly is the first addition to the core web technologies that is already supported in all major web browsers. WebAssembly is a binary and text assembly-like format that enabled native code to run inside the web browsers, which enables safer applications which higher performance. Currently WebAssembly applications are mostly written in C and C++, but work is being done to enable garbage collected languages such as Java and JavaScript to be compile to WebAssembly.

%Earlier work on what today is WebAssembly is what resulted in 

EmScripten \parencite{Zakai2011}, a compiler based on LLVM \parencite{LattnerAdve2014} that originates as a source-to-source compiler from JavaScript to asm.js \parencite{Zakai2011} has been further developed \parencite{HaasRossbergSchuffTitzerHolmanGohmanWagnerZakaiBastien2017} and is now able to compile to both asm.js \emph{and} WebAssembly.

%EmScripten is the most common compiler to compile WebAssembly.

WebAssembly is the result of joint research and development between Apple, Google, Microsoft and Mozilla \parencite{HaasRossbergSchuffTitzerHolmanGohmanWagnerZakaiBastien2017}. WebAssembly has as the first technology since JavaScript full support in Chrome, Edge, Firefox and Safari and could as such be described as the forth core web technology (Figure \ref{webtechnologies-timeline}). Those web browsers that does not support WebAssembly can use asm.js as polyfill \parencite{HaasRossbergSchuffTitzerHolmanGohmanWagnerZakaiBastien2017}. WebAssembly is already being used where performance is of high importance, such as to generate cryptocurrency \parencite{RuthZimmermannWolsingHohlfeld2018}.

Initially WebAssembly supports code written in C/C++ \parencite{HaasRossbergSchuffTitzerHolmanGohmanWagnerZakaiBastien2017}. 
The focus on C/C++ is largely based on WebAssembly implementation limitations such as the lack of garbage collection. According to \textcite{HaasRossbergSchuffTitzerHolmanGohmanWagnerZakaiBastien2017} its a highly prioritized goal to allow WebAssembly to gain to access the web browsers built in garbage collector and that way support languages that use garbage collection.

WebAssembly is loaded as a module via a JavaScript API or another WebAssembly module \parencite{HaasRossbergSchuffTitzerHolmanGohmanWagnerZakaiBastien2017}. It's \emph{not} a goal to have WebAssembly replace JavaScript\footnote{https://webassembly.org/docs/faq/\#is-webassembly-trying-to-replace-javascript}, the idea is that they \emph{complement} each other. One example of how JavaScript and WebAssembly could complement each other is to port selected parts of a popular framework or web app for improved performance without changing it's interface.
%%%

%It's important to notice that WebAssembly in it's current form is a new technology with a few serious limitations (REF). 

%There is also certain things that cannot be done using Wasm.

%dom-manipulation (has to go through javascript)
%passing strings (workarounds can be engineerd)
%invoking wasm-modules from other wasm-modules

%WebAssembly is new technology. The first articles about WebAssembly was published in 2017 \parencite{HaasRossbergSchuffTitzerHolmanGohmanWagnerZakaiBastien2017,ReiserBlaser2017}.

% https://caniuse.com/#feat=wasm